qcircuit 2.5.3 Tutorial

### 2017-11-04 CO681-QuantumInformationProcessing/assignments/assignment_03.tex
starting 4a

\end{document}

>>>>

\section{}
\subsection{a}
The density matrix for $\alpha\ket{00} + \beta\ket{11}$ is
$$\rho = |\alpha|^2\ket{00}\bra{00} + \alpha\beta^*\ket{00}\bra{11} + \alpha^*\beta\ket{11}\bra{00} + |\beta|^2\ket{11}\bra{11}.$$
The partial trace operator $Tr_1$ is defined by matrices $A_0 = \ket{0} \otimes I$ and $A_1 = \ket{1} \otimes I$. Now we compute
$$A_0\rho A_0^\dagger + A_1\rho A_1^\dagger = $$
\end{document}
